Association between trauma severity models and opportunities for improvement:

### 2022-09-23 studyprogressreport.Rmd
made ofi_diagram() a bit better perhaps

---
title: 'Association between trauma severity models and opportunities for improvement:
  A retrospective cohort study'
author: "Victoria Witthoff"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
    number_sections: true
bibliography: bibliography.bib
csl: vancouver.csl
fontsize: 11pt
linestretch: 1
always_allow_html: yes
---

>>>>

---
title: 'Association between trauma severity models and opportunities for improvement:
  A retrospective cohort study'
author: "Victoria Witthoff"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
    number_sections: true
bibliography: bibliography.bib
csl: vancouver.csl
fontsize: 11pt
linestretch: 1
always_allow_html: yes
---
